Investigating the Applications and Limits of Single asymmetric Particle Light Scattering using Limited Detection Schemes

### 2022-11-09 Manuscript.tex
Add files via upload

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[final,3p, twocolumn]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb, amsthm}
\usepackage{amsmath}
%% The amsthm package provides extended theorem environment
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

@@

\title{Investigating the applications and limits of single particle light scattering using limited detection schemes}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

@@

\cortext[cor1]{Corresponding author}
\affiliation[aff1]{organization={Department of Chemical Engineering,
			University of Strathclyde},
            addressline={16 Richmond Street}, 
            city={Glasgow},
            postcode={G1 1XQ}, 
            country={Scotland}}

\begin{abstract}
While optical trapping is a well understood method for force transduction and detection,characterisation of trapped entities poses a two-fold challenge - one experimental concerning the arrangement of light detectors and the other, theoretical involving solving of the inverse light scattering problem. Combining static light scattering techniques with optical trapping poses significant engineering challenges due to the space constraints in a conventional optical trapping setup. We propose here a plausible scenario of detecting scattered light from an optically trapped asymmetric microstructure using a novel, multi-angle, optical-fibre based detection scheme and demonstrate how a Bayesian inference based analysis of the data simulated to mimic light scattering detection signals in such scenarios maybe used for solving the inverse light scattering problem and help characterise trapped entitites. To this end, we discuss the application of our method to infer the instantaneous orientations of an asymmetric microsphere dimer being trapped. We argue that this method can be extended for determining any characteristics of the trapped microstructure that influence the light scattering pattern.

\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
	\centering
	\includegraphics[width=0.8\textwidth, height = 0.6\textheight]{fig1a.png}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Asymmetric dimers of undergo a full inversion in the presence of an potential well
\item Orientation can be classified by applying Bayesian Statistics to light intensity readings
\item Bayesian model shows increased accuracy when processing noisy signal measurements. 
\item Multiple estimations can be  used to cancels out artefacts of noise. 
\end{highlights}

\begin{keyword}
	Optical Trapping \sep Light Scattering \sep Measurements \sep Bayesian Statistics

\end{keyword}

@@

%%\linenumbers

%% main text
\section{Introduction}
\label{1}

\indent Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to those that test the fundamental assumptions of Quantum Mechanics  \cite{yin2013large} thanks mainly to the ability of the tweezer to transduce and detect forces in the order of a few piconewton. Recent applications of the Optical Tweezers in metrological measurements \cite{arita2020coherent} and colloidal aggregation \cite{burns1990optical} demand the tweezer to also be able to characterise  the trapped entity. To this end, chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering \cite{gupta2014raman} and dynamical characterisation has been achieved mainly by following the centre-of-mass brownian motion of the trapped entity using a Quadrant Photo Detector \cite{friedrich2012tuning}. While this technique has allowed for detection of linear motion of trapped entities  with sub-nanometre precision \cite{friedrich2012tuning} and  rotation \cite{yifat2021facile} of the centre-of-mass, there is a paucity of literature on measuring the orientation of trapped non-spherical particles till the recent attempt in \cite{raudsepp2022estimating} where imaging was employed to study the orientation of trapped dimers and a resolution of () was achieved.

Possibility of integrating light scattering with optical trapping was demonstrated by Saffran and 
co-workers in \cite{Bar-Ziv_1998} where a single-mode optical fibre was aligned to detect the scattered light from a trapped bead and it's brownian motion was studied. While this allowed for studying the dynamics, any information with regards structure of the trapped bead was precluded as the measurement was a single-angle scattering measurement.
In this work, we propose a novel Bayesian Inference based technique to interpret light scattering data detected in a scheme that expands on the technique in \cite{Bar-Ziv_1998} to detect scattered light simultaneously at 3 angles as shown in Figure 1.

\section{Theory}
\label{2}

Consider a dimer with unequal sphere diameters $a_1, a_2$ in an optical trap positioned in some orientation $\hat{s}$. Due to the Brownian motion from the surrounding fluid the dimer's orientation changes with time. Assuming we cannot accurately determine the dimer's orientation from imaging alone we instead rely on it's light scattering. We collect the near field intensity, via optical fibres,from a probe laser at 3 angles $\theta_1, \theta_2, \theta_3$. To classify the particle's orientation we compare the produced light scattering signal to a collection of reference orientations that are evenly spaced around the orientation space.

\begin{figure}[t]
	\centering
	\includegraphics[width = 0.5\textwidth]{junk_00078.png}
	\caption{Reference orientations plotted in the physical space. Green arrow points in the direction of the dimers orientation. The red point is our estimation, and the green point is the best possible estimate.}
\end{figure}

We use the a Fortran package specialised for calculating non spherical t-matrices (MSTM) \cite{Mishchenko1996MSTM} to determine the light scattering intensity of our dimer in each reference orientation. We assume that the for each detection fibre the intensities can be distributed on a Gaussian curve centred at $y_k$, the normalised intensity at detection fibre k. Based on the light scattering from the dimer we can assign a probability that the produced light scattering pattern produced belongs to the reference orientation $\hat{n}$

\begin{align}
	p(y(\hat{s})\parallel\hat{n}) =& \Pi^3_{k=1}
	(2\pi\sigma_k^2)^{-1/2} \nonumber \\     &e^{-(y(\hat{n})_k-y(\hat{s})_k)^2/2\sigma_k^2}
\end{align}

Where $\sigma_k$ is the average error in our signal collection; we left this as a tuneable variable to measure how the influence of signal error would effect our predictive model. This was implemented by adjusting the values of $y(\hat{s}_k)$.

\begin{align}
	\centering
	\sigma_k =& 0.17\bar{y}(\hat{n}_k) \\
	\Rightarrow y(\hat{s}_k) =& y(\hat{s})_k \pm n\sigma_k \\ 
	n \in \mathbb{R}, \ \ & n\in[0,1] \nonumber
\end{align}

We can view this result as a conditional probability, if the orientation is determined ($\hat{n}$) then what is the probability that expected scattering signal matches our dimer's scattering signal. We instead want to know the inverse conditional, that with a given signal y the dimer was in orientation $\hat{n}$. We can calculate this using Bayes' theory:

@@

\subsection{Testing the model}
\label{2.1}
We use the Brownian OT package by Jerome Fung \cite{Vigilante2020Brownian_OT} to simulate how our target dimer moves while subject to an optical trap. At each time step we determine the dimer's orientation and use MSTM to calculate its scattering pattern. We then use the above method to estimate the dimer orientation based on its scattering pattern. The priori estimate $p(\hat{n})$ can be defined as a Boltzmann's distribution based on the normalised dot product of our previous estimation $\hat{n}_{t-\Delta t}$ and each reference orientation $\hat{n}_t$:

\begin{align}
	r_j(t, \hat{n})= \frac{1}{2}((\hat{n}_{t} \cdot \hat{n}_{t-\Delta t})-1) \\
	p(\hat{n})= \frac{e^{\beta (r_j(t,\hat{n})-1)}}
	{\Sigma_{i=1}^{24}e^{\beta(r_i(t, \hat{n}))}}
\end{align}

@@

Where the divergence goes to zero if $p_{ideal}=0$, for a single estimation this gives us an idea of both how confident our model is in it's estimation. We sum the divergence of each measurement across the entire simulation to get an idea of how well the model performs across the entire simulation. To measure how much our result had improved we compare it to a worse case scenario, where every $\hat{n}$ is given uniform probability, and evaluate the improvement factor $F(K_l)$

\begin{align}
	K_{l,total} = \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
	F(K_l) = \frac{K_{l,\ worst}}{K_{l,total}}
\end{align}

To measure how much our result had improved we compare it to a worse case scenario, where every $\hat{n}$ is given uniform probability. Since our divergence result is a product of our choice of angles we can see analyse how the choice of angles can be altered to improve our estimate.

\subparagraph{Optimization of parameters}
\label{2.2}
The efficacy of our estimation is a function of our detection angles, testing every possible configuration manually is time consuming, therefore we utilised Ultra nest to apply a Monte Carlo simulation to our model. Ultra-nest is a sophisticated python package for fitting models with complex parameter interactions \cite{Buchner2016Ultranest}. Ultra-nest implements a variation of Monte Carlo integration,nested-sampling, where the likelihood contour is used to update a group of live points chosen from the prior estimation ($0^{\circ} \leq \theta_k \leq 180^{\circ}$).

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{traj.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{pos.png}
	\end{subfigure}
	\caption{Simulation results of: a) the dimers orientation vector with time, b) the dimer's [x,y,z] position with time.}
\end{figure}

@@

\subsection{Predictive efficacy of model}
\label{3.2}
The data from \figurename{ 2a} was used to test the efficacy of our predictive model. To visualise how well our model tracks the dimer's orientation we plot the radial distance between our model's prediction and the true orientation, and between the best possible orientation and the true orientation. For a perfect estimation these two plots should overlap.

We first tested how varying the error value would effect our model's efficacy; calculating the improvement factor $F(K_l)$ with each test, the measurements were made with detection angles of $15^{\circ}, \ 45^{\circ}, \ \& \ 90^{\circ}$. As can be seen from \figurename{ 3} our model actually performs better with noisy signals, to the extent that there was a 0.2 difference between our estimation with $10 \%$ signal error and $30\%$. The reasoning for this being that a noisy signal means that any time our model deviates from the correct response it will quickly self correct due to the larger variance.  The issue with having a high signal error is that our model's prediction can be very far off from the correct answer and still be confident with it's results; fortunately our priori for the dimer's orientation can help to correct our estimate by limiting the probability in the physical space. We found that the inclusion of our priori estimate compared to a uniform priori improved our results by around $20 \%$.

\begin{figure}[t]
	\centering
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{Error_10_percent.png}
		\subcaption{$F(K_l) = 0.9422$}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{Error_20_percent.png}
		\subcaption{$F(K_l) = 1.366$}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{Error_30_percent.png}
		\subcaption{$F(K_l)=1.440$}
	\end{subfigure}
	\caption{Model predictions with signal error at a) $10 \%$, b)  $20\%$, and c) $30\%$. Dotted line represents minimum distance between reference orientations}
\end{figure}

We estimate that at minimum our experimental setup should have a $17\%$ signal error, assuming near perfect alignment of fibres and minimal interference from other microspheres in the solution. Therefore the fact that our model provides a better estimation of the dimer's motion with worse noise is promising for the implementation of our model into a experimental setup. To assess the impact of signal error, angle choice, and weighting factor we utilised ultranest to step through the entire parameter space.

\subsection{Ultra-nest results}
\label{3.3}
We first wanted to measure analyse the impact of our choice of angles in our predictive model.

\begin{figure} [t]
	\centering
	\includegraphics[width=0.4\textwidth]{Cornerangleconstrained-1.png}
	\caption{Corner plot from ultra-nest, darker regions indicate a better divergence result. $\theta_1$ was constrained between $15^{\circ}$ and $25^{\circ}$; $\theta_2$ was constrained between $30^{\circ}$ and $60^{\circ}$; $\theta_3$ was constrained between $65^{\circ}$ and $100^{\circ}$.}
\end{figure}

As can be seen from \figurename{ 4} the parameter space for our angle choice is essentially flat, with no explicit maxima to be found, the sudden increase in our divergence around $\theta_1 = 18^{\circ}$ is likely due to the fact that if we consider the scattering curves for our reference orientations there exist local minima on at roughly $\theta_1 = 13^{\circ}$ and $25^{\circ}$. Therefore between these two minima the model struggles to differentiate between reference orientations given that the light intensity is similar for different orientations.

We then decided to remove the limitations on our choice of angles, the only constraining factor being that the fibre's could not be placed within $10^{\circ}$ of each other.

\begin{figure} [h]
	\centering
	\includegraphics[width=0.4\textwidth]{corneranglesfreed-1.png}
	\caption{Corner plot from ultra-nest, darker regions indicate a better divergence result. Choice of angles is not limited to a predefined region.}
\end{figure}

Now we see that allowing the angles to be anywhere in the parameter space results in a more focused result for both $\theta_2$ and $\theta_3$ but still a flat parameter space for $\theta_1$. The result suggests that the model is more successful when we allow for backscattering to be considered in our model. While this works for a perfect system where noise is a known quantity it is unlikely if the signals are clear enough under laboratory conditions.

@@

\bibliography{bib} 
\bibliographystyle{ieeetr}
\end{document}
\endinput

>>>>

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[preprint,3p]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb, amsthm}
\usepackage{amsmath}
%% The amsthm package provides extended theorem environment
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

@@

\title{Investigating the Applications and Limits of Single asymmetric Particle Light Scattering using Limited Detection Schemes}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%Saffran
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

@@

\cortext[cor1]{Corresponding author}
\affiliation[aff1]{organization={Department of Chemical Engineering,
			University of Strathclyde},
            addressline={75 Montrose Street}, 
            city={Glasgow},
            postcode={G1 1XL}, 
            country={Scotland}}

\begin{abstract}
While optical trapping is a well understood method for force transduction and detection,characterisation of trapped entities poses a two-fold challenge - one experimental concerning the arrangement of light detectors and the other, theoretical involving solving of the inverse light scattering problem. Combining static light scattering techniques with optical trapping poses significant engineering challenges due to the space constraints in a conventional optical trapping setup. We propose here a plausible scenario of detecting scattered light from an optically trapped asymmetric microstructure using a novel, multi-angle, optical-fibre based detection scheme and demonstrate how a Bayesian inference based analysis of the data simulated to mimic light scattering detection signals in such scenarios maybe used for solving the inverse light scattering problem and help characterise trapped entities. To this end, we discuss the application of our method to infer the instantaneous orientations of an asymmetric microsphere dimer being trapped. We argue that this method can be extended for determining any characteristics of the trapped microstructure that influence the light scattering pattern.
\end{abstract}
%%Research highlights
\begin{highlights}
\item Asymmetric dimers of undergo a full inversion in the presence of an potential well
\item Orientation can be classified by applying Bayesian Statistics to light intensity readings
\item Bayesian model shows increased accuracy when processing noisy signal measurements. 
\item Multiple estimations can be  used to cancels out artefacts of noise. 
\end{highlights}

\begin{keyword}
	Optical Trapping \sep Light Scattering \sep Measurements \sep Bayesian Statistics \sep Theoretical 
\end{keyword}

@@

\linenumbers

%% main text
\section{Introduction}
\label{sec:Intro}

\indent Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to those that test the fundamental assumptions of Quantum Mechanics  \cite{yin2013large} thanks mainly to the ability of the tweezer to transduce and detect forces in the order of a few piconewton. Recent applications of the Optical Tweezers in metrological measurements \cite{arita2020coherent} and colloidal aggregation \cite{burns1990optical} demand the tweezer to also be able to characterise  the trapped entity. To this end, chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering \cite{gupta2014raman} and dynamical characterisation has been achieved mainly by following the centre-of-mass Brownian motion of the trapped entity using a Quadrant Photo Detector \cite{friedrich2012tuning}. 
\begin{wrapfigure}[12]{r}{0.3\textwidth}
	\centering
	\includegraphics[width=0.3\textwidth]{fig1a}
	\caption{Experimental set up}
	\label{fig:1}
	\vspace{-100pt}
\end{wrapfigure}
While this technique has allowed for detection of linear motion of trapped entities  with sub-nanometre precision \cite{friedrich2012tuning} and  rotation \cite{yifat2021facile} of the centre-of-mass, there is a paucity of literature on measuring the orientation of trapped non-spherical particles till the recent attempt in \cite{raudsepp2022estimating} where imaging was employed to study the orientation of trapped dimers and a resolution of () was achieved.   
Possibility of integrating light scattering with optical trapping was demonstrated by Saffran and co-workers in \cite{Bar-Ziv_1998} where a single-mode optical fibre was aligned to detect the scattered light from a trapped bead and it's Brownian motion was studied. While this allowed for studying the dynamics, any information with regards structure of the trapped bead was precluded as the measurement was a single-angle scattering measurement.
\newpage
In this work, we propose a novel Bayesian Inference based technique to interpret light scattering data detected in a scheme that expands on the technique in \cite{Bar-Ziv_1998} to detect scattered light simultaneously at 3 angles as shown in Figure~\ref{fig:1}.

\section{Theory}
\label{sec:Theory}

Consider a dimer with unequal sphere diameters $a_1, a_2$ in an optical trap in some orientation $\hat{s}$. Due to the Brownian motion from the surrounding fluid the dimer's orientation changes with time. Assuming we cannot accurately determine the dimer's orientation from imaging alone we instead rely on it's light scattering. Rather than directly calculate the orientation vector we instead discretise the orientation space into 30 reference orientations. See \ref{Appendix 1} for the exact numerical values of reference orientations. The following records how we apply a Bayesian model to determine the estimate the closest reference orientation based on an instantaneous light scattering measurement.

We use a Fortran package specialised for calculating non spherical t-matrices (MSTM) \cite{Mishchenko1996MSTM} to determine the light scattering intensity of our dimer in each reference orientation. The raw signal intensities for at 3 different angles ($\theta_1, \ \theta_2, \ \& \ \theta_3$) are calculated and then scaled down so that the signal response $y_k$ is normalised for each angle $k$:

\begin{align}
	y_k(\hat{n}) = 
	 \frac{\left[I(\hat{n}, \ \theta_k)- \langle I(\hat{n}, \ \theta_k) \rangle \right]} 
	{\langle I^2(\hat{n},\ \theta_k) \rangle -\langle I(\hat{n}, \ \theta_k)\rangle^2}
\end{align}

See \ref{Appendix 1} for a breakdown of the raw intensities and scaled signal responses. To classify the particle's orientation we compare the produced light scattering signal to a collection of reference orientations that are evenly spaced around the orientation space. We assume that the for each detection fibre the intensities can be distributed on a Gaussian curve centred at $y_k$, the normalised intensity at detection fibre k. Based on the light scattering from the dimer we can assign a probability that the produced light scattering pattern belongs to the reference orientation $\hat{n}$

\begin{align}
	p(y(\hat{s})\parallel\hat{n}) =& \Pi^3_{k=1}
	(2\pi\sigma^2)^{-1/2} \nonumber \\     &e^{-(y(\hat{n})_k-y(\hat{s})_k)^2/2\sigma^2}
\end{align}

Where $\sigma$ is the minimum distance between our reference orientations signals ($y_1, \ y_2, \ \& \ y_3$), . We can view this result as a conditional probability, if the orientation is determined ($\hat{n}$) then what is the probability that expected scattering signal matches our dimer's scattering signal. We instead want to know the inverse conditional, that with a given signal y the dimer was in orientation $\hat{n}$. We can calculate this using Bayes' theory:

@@

\subsection{Brownian Simulation}
\label{sec:2.1}
We use the Brownian OT package by Jerome Fung \cite{Vigilante2020Brownian_OT} to simulate how our target dimer moves while subject to an optical trap. The package is unique in that it combines MSTM \cite{Mishchenko1996MSTM} and 'Optical Tweezer Toolbox' (\textit{ott}) to simulate the motion of arbitrary shaped particles.

For any trapped particle their are two major sources of motion, Brownian motion and optical forces. The Brownian displacement ($\Delta q^{\textbf{B}}$) is approximated by generating a set of normally-distributed numbers whose covariance is given by the dimer's diffusion tensor $\textbf{D}$. The diffusion tensor is computed based on Farsund's work \cite{Farsund1996}.

\begin{align}
	\langle \Delta q_i^{\textbf{B}} \Delta q_j^{\textbf{B}}\rangle &= 2D_{ij} \Delta t 
\end{align}

For computing the optical force Brownian OT uses the T-Matrix method to calculate the scattering coefficients of the outgoing scattered wave. The T-matirx describes the scattering process by relating the scattering wave to the incident wave in an elegant equation.

\begin{align}
	\begin{pmatrix}
		p_{mn} \\
		q_{mn}
	\end{pmatrix}
	= \textbf{T}
	\begin{pmatrix}
		a_{mn} \\
		b_{mn}
	\end{pmatrix}
\end{align}

MSTM computes the T-matrix of the dimer, and then passes the T-matrix to \textit{ott} to compute the optical forces. The benefit of this approach is that MSTM can accurately compute the T-matrix for the dimer once and then \textit{ott} can calculate the optical force after each time step. The dimer displacement is the sum of both the optical and Brownian contributions. Brownian OT returns the displacement as a trajectory file; with the [x,y,z] position being relative to the trap focus, and the orientation being returned as a quaternion.

For our model we simulate the motion of silica dimer trapped in a 5mW Gaussian beam; the dimer is comprised of two spheres with radii $1\\mu m, \ \& 0.5 \ \mu m$ respectively.

\subsection{Testing our Model}
\label{sec:2.2}

Since MSTM has computed the T-matrix for our dimer, we can reuse it to calculate. We then apply \eqref{3} - covered in Section~\ref{sec:2.1} - to estimate the dimer orientation based on its scattering pattern. The priori estimate $p(\hat{n})$ is defined as a Boltzmann's distribution based on the normalised dot product of our previous estimation $\hat{n}_{t-\Delta t}$ and each reference orientation $\hat{n}_t$:

\begin{align}
	r_j(t, \hat{n})= \frac{1}{2}((\hat{n}_{t} \cdot \hat{n}_{t-\Delta t})-1) \\
	p(\hat{n})= \frac{e^{\beta (r_j(t,\hat{n})-1)}}
	{\Sigma_{i=1}^{30}e^{\beta(r_i(t, \hat{n})-1)}}
\end{align}

@@

Where the divergence goes to zero if $p_{ideal}=0$, for a single estimation this gives us an idea of how confident our model is in it's estimation. We sum the divergence of each measurement across the entire simulation to get an idea of how well the model performs across the entire simulation. To measure how much our result had improved we compare it to a worse case scenario, where every $\hat{n}$ is given uniform probability, and evaluate the improvement factor $F(K_l)$

\begin{align}
	K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#} \\
	K_{l, \ worst} &= -\sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/30} \right] \\
	F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

The worst case scenario can be akin to randomly choosing a reference orientation at each time step. Because our model is dependent on several parameters at once we need to a more sophisticated method for finding the optimum choice of parameters.

\subparagraph{Optimization of parameters}
\label{2.3}
The efficacy of our estimation is a function of our detection angles, signal error, and weighting of $p(\hat{n})$. Evaluating every possible configuration manually is inefficient, therefore we utilised Ultra nest to apply a Monte Carlo simulation to our model. Ultra-nest is a sophisticated python package for fitting models with complex parameter interactions \cite{Buchner2016Ultranest}. Ultra-nest implements a variation of Monte Carlo integration, nested-sampling, where the likelihood contour is used to update a group of live points chosen from the prior estimation ($0^{\circ} \leq \theta_k \leq 180^{\circ}, \ 0 \leq \epsilon \leq 1, \ 0 \leq \beta \leq 5$).

@@

\begin{figure}[t]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/traj.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/pos.png}
	\end{subfigure}
	\caption{Simulation results of: a) the dimers orientation vector with time, b) the dimer's [x,y,z] position with time.}
\end{figure}

@@

\newpage
\subsection{Predictive efficacy of model}
\label{sec:3.2}
The data from \figurename{ 2a} was used to test the efficacy of our predictive model. To visualise how well our model tracks the dimer's orientation we plot the radial distance between our model's prediction and the true orientation, and between the best possible orientation and the true orientation. For a perfect estimation these two plots should overlap. Overall their our three main factors that effect the performance of our prediction; the signal error $\sigma$, our choice of angles $\theta_1, \theta_2, \ \& \theta_3$, and our weighting factor $\beta$.

We tested how changing our weighting factor for a set choice of angles would influence the performance of our model.  We first set our choice of angles to $15^{\circ}, \ 45^{\circ},\ \& \ 90^{\circ}$ and varied $\beta$ between 0.5-1.5.

\begin{figure}[b]
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{./Images/154590_Beta=1.png}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{./Images/154590_Beta=05.png}
	\end{subfigure}
	\begin{subfigure}{0.33\textwidth}
		\includegraphics[width=\textwidth]{./Images/154590_Beta=15.png}
	\end{subfigure}
\end{figure}

\newpage
\subsection{Ultranest Results}
\label{3.3}
We wanted to see if our choice of angles plays a significant role in our model's efficacy. We employed ultranest to analyse the parameter space for our three angles by sampling across the priori of $10^{\circ} \ \& \ 180^{\circ}$. We kept both $\beta$ and $\sigma$ constant during this so we could as these are parameters that can be changed more freely.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{corneranglesfreed-1.png}
	\caption{Corner plot mapping combinations of $\theta$ that generate the best improvement}
\end{figure}

\figurename{ 4} is the resulting corner plot from our ultranest sampler, darker areas indicate a choice of angles where the model performed better where as lighter areas are where the model did poorer. Overall from the corner plot provided it's clear that there is no direct correlation between our model's performance and the choice of detection angle. While the choice of angles does not provide a direct improvement in our estimation it does determine how finely we can estimate the orientation, for choices of angles that are close together the minimum spacing between our signals is so small that we can't achieve any greater accuracy than dividing the orientation space into 30 reference orientations. We hope to develop our model further in the future by being able to determine the maximum accuracy given that we know the signal error of our measurements.

As covered in \ref{sec:3.2} our choice for beta can help to improve our estimation somewhat by limiting our estimation in the physical space.

@@

\bibliography{bib} 
\bibliographystyle{ieeetr}
\newpage

\section*{Appendix}
\label{Appendix 1}
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:n} Reference Orientations vector components$^*$}
		\begin{tabular}{|c|c|c|c|}
			\hline\hline
			Reference Orientation & $\hat{n}_x$ &  $\hat{n}_y$ &  $\hat{n}_z$ \\
			\hline
			$1$ & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
			$2$ & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
			$3$ & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
			$4$ & $1.0000$ &  $0.00000$ & $0.00000$ \\
			$5$ & $0.00000$ &  $1.0000$ & $0.00000$ \\
			$6$ & $0.00000$ &  $0.00000$ & $1.0000$ \\
			$7$ & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
			$8$ & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
			$9$ & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
			$10$ & $0.00000$ &  $0.00000$ & $-1.0000$ \\
			$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
			$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
			$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
			$14$ & $0.00000$ &  $-1.0000$ & $0.00000$ \\
			$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
			$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
			$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
			$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
			$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
			$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
			$21$ & $-1.0000$ &  $0.00000$ & $0.00000$ \\
			$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
			$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
			$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
			$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
			$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
			$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
			$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
			$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
			$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
			\hline\hline
			\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\end{table}
